Data preparation

### 2023-09-19 procesamiento/prod_analysis.Rmd
ajuste modelos

```{r redistribution}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
load(here::here("input/data/proc/study1.RData"))
df1$country<- as.numeric(df1$country)
df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
df1$redistF <- factor(df1$redist,levels = 1:5,labels = sjlabelled::get_labels(df1$redist))
percentage_data <- df1 %>%
  group_by(country2, redistF) %>%
  summarise(count = n()) %>%
  group_by(country2) %>%
  na.omit() %>% 
  mutate(percentage = count / sum(count)) %>% 
  arrange(country2,redistF,percentage) %>% 
  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
  mutate(pct_lab=ifelse(!redistF %in% c("Strongly agree"),NA,pct_lab))

order <- 
percentage_data %>% 
  filter(redistF=="Strongly agree") %>% 
  arrange(percentage) %>% 
  select(country2)

@@

```{r correlation-segregation}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2)
load(here::here("input/data/proc/study1.RData"))
# df1$class6 <- forcats::fct_rev(factor(df1$class6,ordered = T))
cormat1 <- 
df1 %>% 
    select('redist',homclass,homclass_s,homclass_w,pi_nteg,class3) %>% 
  na.omit() %>% 
  polycor::hetcor(parallel = T)

@@

```{r}
df1$country2 <- sjlabelled::to_character(df1$country)
library(scales)

@@

# Modelos

dicotomizar homogeneidad en 1=50% similar,49% similar

```{r isei}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(sjmisc,ggplot2,lme4,interplot)
load(here::here("input/data/proc/study1.RData"))
# remove.packages("Matrix")
# install.packages("Matrix")
df1$class3<-forcats::fct_rev(df1$class3)
df1$class5<-forcats::fct_rev(df1$class5)
df1$class6<-forcats::fct_rev(df1$class6)
dfreg <- df1 %>% dplyr::select(redist,
                        isei08,
                        eindex,
                        prestige,
                        diversity,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        ednum,female,agenum,country) %>% na.omit()

dfreg$country <- to_factor(dfreg$country)
dim(dfreg)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ eindex + (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + isei08+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + isei08+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1+female+agenum+isei08+ednum+prestige+diversity+eindex+(1|country),data=dfreg)
full_int1 <- lmer(redist~1+female+agenum+eindex*isei08+(1|country),data=dfreg)
full_int2 <- lmer(redist~1+female+agenum+prestige+diversity+eindex*isei08+ednum+(1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

texreg::plotreg(full,omit.coef = "(Intercept)")

interplot::interplot(m = full_int1,var1 = "eindex",var2="isei08") +
  ylab("Network diversity coefficient")+
  xlab("SES Respondent")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

#-----------
dfreg <- df1 %>% select(redist,
                        isei08,
                        eindex,
                        prestige,
                        # diversity,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        ednum,female,agenum,country) %>% na.omit()

dim(dfreg)
base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)

class <- lmer(redist~1+female+agenum+isei08+(1|country),data=dfreg)
class_status <- lmer(redist~1+female+agenum+isei08+ednum+(1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1|country),data=dfreg)
fullrs <- lmer(redist~1 +female+agenum + isei08 +ednum +  prestige + eindex +(1+eindex|country),data=dfreg)
full_int1 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1|country),data=dfreg)
full_int2 <- lmer(redist~1+female+agenum+prestige+eindex*isei08+ednum+(1+eindex|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

texreg::plotreg(full, omit.coef = "(Intercept)")

interplot::interplot(m = full_int2,var1 = "eindex",var2="isei08") +
  ylab("Network heterogeneity coefficient")+
  xlab("SES Respondent")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_diversityxisei.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
# en la medida que aumenta el status, el efecto de la diversidad de la red se vuelve positivo.
# en personas de estatus bajo la diversidad hace que demanden menos redistribucion
# en personas de estatus alto la diversidad hace que demanden más redistribucion
```

```{r class-diversity}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
load(here::here("input/data/proc/study1.RData"))

levels(df1$class3)
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
levels(df1$class3)
levels(df1$class5)
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))

df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
levels(df1$class6)

dfreg <- df1 %>% select(redist,
                        class6,
                        class3,
                        class5,
                        # eindex,
                        prestige,
                        diversity,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        ednum,female,agenum,country) %>% na.omit()
dim(dfreg)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class6 +ednum +  prestige + diversity +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class6+ ednum + (1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + diversity +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class5+ ednum + (1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
diversity <- lmer(redist~1 + female+agenum + prestige + diversity+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + diversity +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity*class3+ ednum + (1+diversity|country),data=dfreg)
models <- list(prestige,diversity,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

interplot::interplot(m = full_int1,var1 = "diversity",var2="class3") +
  ylab("Network diversity coefficient")+
  xlab("SES Respondent")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

@@

```{r class-homclass}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot)
load(here::here("input/data/proc/study1.RData"))

df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))

df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,
                        class3,
                        class5,
                        # eindex,
                        # know_total,
                        homclass,
                        # homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,
                        # sstatus,
                        giniwd,
                        ednum,female,agenum,country) %>% na.omit()
dim(dfreg)
dfreg$country <- to_factor(dfreg$country)

sjPlot::plot_model(lmer(redist~1 + female+agenum + homclass*giniwd + pi_nteg+class3 +ednum + Q05pcm + giniwd + (1+homclass|country),data=dfreg),show.values = T)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + homclass+ (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +ednum+homclass + pi_nteg + Q05pcm + (1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + homclass*class3+ pi_nteg+ ednum +(1|country),data=dfreg)
full_int3 <- lmer(redist~1 +female+agenum + homclass+pi_nteg*class3+ pi_nteg+ ednum + (1|country),data=dfreg)

models <- list(homclass,class,class_status,full,full_int1,full_int3)
texreg::knitreg(models)
texreg::knitreg(full)
sjPlot::plot_model(full,show.values = T,rm.terms = c("ednum","femaleFemale","agenum")) + geom_hline(yintercept = 0)
ggsave(plot = last_plot(),filename = "model_full.png",device = "png",
       path = here::here("output"),width = 1.5,height = 1,units = "cm",scale = 15)

interplot <- 
interplot::interplot(m = full_int2,var1 = "homclass",var2="class3")

df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Class-based homogeneity coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_homoxclass.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)

isolation <- 
interplot::interplot(m = full_int3,var1 = "pi_nteg",var2="class3")
df_int2 <- isolation$data
df_int2 <- df_int2[c(1,2,4),]
df_int2$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int2
df_int2$value <- factor(df_int2$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int2 %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Perceived isolation coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_isolationxclass.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
```

```{r eindex}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,lme4)
load(here::here("input/data/proc/study1.RData"))

levels(df1$class3)
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
levels(df1$class3)
levels(df1$class5)
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))

df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
levels(df1$class6)

dfreg <- df1 %>% select(redist,
                        class6,
                        class3,
                        class5,
                        eindex,
                        homclass,
                        # homclass_s,homclass_w,
                        prestige,
                        diversity,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        ednum,female,agenum,country) %>% na.omit()

dim(dfreg)
cor(dfreg[,c("eindex","prestige","diversity")])

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
eindex <- lmer(redist~1 + female+agenum + prestige +diversity+eindex+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class6+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class6+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class6 +ednum + prestige +diversity+ eindex +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+diversity+eindex*class6+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+diversity+eindex*class6+ ednum + (1+eindex|country),data=dfreg)
models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
eindex <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class5+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class5+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class5 +ednum +  prestige + eindex +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+eindex*class5+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+eindex*class5+ ednum + (1+eindex|country),data=dfreg)
models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

base <- lmer(redist~1 + (1|country),data=dfreg)
demo <- lmer(redist~1 +female+agenum + (1|country),data=dfreg)
prestige <- lmer(redist~1 + female+agenum + prestige + (1|country),data=dfreg)
eindex <- lmer(redist~1 + female+agenum + prestige + eindex+ (1|country),data=dfreg)

class <- lmer(redist~1 +female+agenum + class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + class3+ednum+ (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + class3 +ednum +  prestige + eindex +(1|country),data=dfreg)
full_int1 <- lmer(redist~1 +female+agenum + prestige+eindex*class3+ ednum +(1|country),data=dfreg)
full_int2 <- lmer(redist~1 +female+agenum + prestige+eindex*class3+ ednum + (1+eindex|country),data=dfreg)
models <- list(prestige,eindex,class,class_status,full,full_int1,full_int2)
texreg::knitreg(models)

interplot <- 
interplot::interplot(m = full_int2,var1 = "eindex",var2="class3") +
  ylab("Network heterophily coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  ylab("Network heterophily coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0)

ggsave(plot = last_plot(),filename = "margins_hetxclass.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 15)
```

>>>>

```{r redistribution}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,GGally,ggplot2)
load(here::here("input/data/proc/study1.RData"))
df1$country<- as.numeric(df1$country)
df1$country2 <- countrycode::countrycode(sourcevar = df1$country,origin = "iso3n",destination = "country.name")
df1$redistF <- factor(df1$redist,levels = 1:5,labels = sjlabelled::get_labels(df1$redist))

df1 %>%
  group_by(country2, ) %>%
  summarise(redist = mean(redist, na.rm = T)) %>% 
  View()

percentage_data <- df1 %>%
  group_by(country2, redistF) %>%
  summarise(count = n()) %>%
  group_by(country2) %>%
  na.omit() %>% 
  mutate(percentage = count / sum(count)) %>% 
  arrange(country2,redistF,percentage) %>% 
  mutate(pct_lab = paste0(round(percentage*100,1),"%")) %>% 
  mutate(pct_lab=ifelse(!redistF %in% c("Strongly agree"),NA,pct_lab))

order <- 
percentage_data %>% 
  filter(redistF=="Strongly agree") %>% 
  arrange(percentage) %>% 
  dplyr::select(country2)

@@

```{r correlation-segregation}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2)
load(here::here("input/data/proc/study1.RData"))
# df1$class6 <- forcats::fct_rev(factor(df1$class6,ordered = T))
cormat1 <- 
df1 %>% 
    select('redist',homclass,homclass_s,homclass_w,pi_nteg,class3,) %>% 
  na.omit() %>% 
  polycor::hetcor(parallel = T)

@@

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,GGally,ggplot2,scales)
load(here::here("input/data/proc/study1.RData"))
df1$country2 <- sjlabelled::to_character(df1$country)
library(scales)

@@

# macro correlations

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,haven)
load(here::here("input/data/proc/study1_country.RData"))
df2$country2 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "country.name")
df2$country3 <- countrycode::countrycode(sourcevar = df2$country,origin = "iso3n",destination = "iso3c")
df2 <- bind_cols(df2,sjmisc::to_dummy(x = df2$class3,suffix = "numeric"))

macro_data <- df2 %>%
  group_by(country2,country3) %>%
  summarise_at(c("redist","homclass","pi_isola","tr_courts","tr_inte","gini_disp","gini_mkt",
                 "class3_1","class3_2","class3_3","gv_spen"), mean, na.rm = TRUE) %>% 
  as.data.frame()

macro_data %>%  
ggplot(aes(y=redist, x=homclass)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Class homogeneity")+
  ylab("Redistributive preferences") +
  labs(title = "Redistributive preferences and Class homogeneity",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$redist, use='complete.obs'),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_homo_redist.png",device = "png",
       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)

macro_data %>%  
ggplot(aes(y=redist, x=pi_isola)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Perceived isolation")+
  ylab("Redistributive preferences") +
  labs(title = "Redistributive preferences and Perceived isolation",
       caption =paste("r=",round(cor(macro_data$pi_isola,
                                     macro_data$redist, use='complete.obs'),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_pisol_redist.png",device = "png",
       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)

macro_data %>%  
ggplot(aes(y=pi_isola, x=homclass)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Class homogeneity")+
  ylab("Perceived isolation") +
  labs(title = "Perceived isolation and Class homogeneity",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$pi_isola),digits = 2)))
ggsave(plot = last_plot(),filename = "macro_homo_pisol.png",device = "png",
       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)

macro_data %>%  
ggplot(aes(y=homclass, x=class3_3)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Working class (%)")+
  ylab("Class homogeneity") +
  labs(title = "Class homogeneity and Working class (%)",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$class3_3),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_working_homo.png",device = "png",
       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)

macro_data %>%  
ggplot(aes(y=homclass, x=class3_2)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Intermediate class (%)")+
  ylab("Class homogeneity") +
  labs(title = "Class homogeneity and Intermediate class (%)",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$class3_2),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_middle_homo.png",device = "png",
       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)

macro_data %>%  
ggplot(aes(y=homclass, x=class3_1)) +
  # geom_point() +
  geom_text(label=as.character(macro_data$country3)) +
  # scale_x_continuous(limits = c(0,1))+
  # scale_y_continuous(limits = c(1,5))+
  geom_smooth(method = "lm",fullrange=TRUE) +
  xlab("Service class (%)")+
  ylab("Class homogeneity") +
  labs(title = "Class homogeneity and Service class (%)",
       caption =paste("r=",round(cor(macro_data$homclass,
                                     macro_data$class3_1),digits = 2)))

ggsave(plot = last_plot(),filename = "macro_service_homo.png",device = "png",
       path = here::here("output"),width = 1,height = 1,units = "cm",scale = 20)

@@

### 2023-09-19 procesamiento/prod_prep-country.Rmd
ajuste modelos

@@

```{r pen-data}
pendata<- haven::read_dta(file = "input/data/original/pen-world/pwt1001.dta")
pendata$ccode <- countrycode::countrycode(sourcevar = pendata$countrycode,origin = "iso3c",destination = "iso3n")
pen <- pendata %>% filter(ccode %in% countries$ccode,year %in% 2017)

@@

```{r merge}
df1$ccode <- as.numeric(df1$country)
df2 <- 
df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","palmawd","rgdpna")],by = "ccode")
```

>>>>

```{r wid-dataset}
wid <- 
  read.csv(file = here::here("input/data/original/wid-percentiles/WID_Data_Metadata/WID_Data_28072023-104940.csv"),sep = ";")
country_data3 <- country_data3 %>% 
  left_join(wid,by="ccode")
summary(country_data3)
```

```{r otero23}
otero <- 
  read.csv(file = here::here("input/data/original/otero23.csv"),sep = ";")
otero$ccode <- countrycode::countrycode(sourcevar = otero$iso3n,origin = "iso2c",destination = "iso3n")
country_data3 <- country_data3 %>% 
  left_join(otero,by="ccode")
summary(country_data3)
```

@@

```{r pen-data}
pendata<- haven::read_dta(file = here::here("input/data/original/pen-world/pwt1001.dta"))
pendata$ccode <- countrycode::countrycode(sourcevar = pendata$countrycode,origin = "iso3c",destination = "iso3n")
pen <- pendata %>% filter(ccode %in% countries$ccode,year %in% 2017)

@@

```{r merge}
df1$ccode <- as.numeric(df1$country)
df2 <- 
df1 %>% left_join(country_data4[,c("ccode","c3","giniwd","gini_disp","gini_mkt","gini","gv_spen","palmawd","rgdpna","pc10_2017","pc50_2017")],by = "ccode")
```
